### 2010-12-13 docs/tex/review.tex
Some more changes...

\section{Artificial Life}
As Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science. In contrast to that, in Artificial Life, scientist take concepts from Biology, specially Evolutionary Biology and genetics and implement into computer science.

@@

\begin{enumerate}
	\item \textsl{``All complex adaptive system involves large number of parts undergoing a kaleidoscopic array of simultaneous non linear interactions."}
	\item \textsl{``The impact of these systems in human affairs centers on the aggregate behavior, the behavior of the whole."}
	\item \textsl{``The interactions evolve over time, as the parts adapt in an attempt to survive in the environment provided by the other parts."}
	\item \textsl{``Complex adaptive systems anticipate."}
\end{enumerate}

@@

\subsubsection{Criteria}
Echo has been constructed on a set of criterion. The following is a short summary on it extracted from Holland's, \textsl{Hidden Order: How Adaptation Builds Complexity} \cite{holland1996}.

@@

\section{Cellular Automata}

\section{Conclusion}

>>>>

\section{Artificial Life}
As Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science. In contrast to that, in Artificial Life, scientist take concepts from biology, specially evolutionary biology and genetics and implement into computer science.

@@

\begin{enumerate}
	\item \textsl{``All complex adaptive system involves large number of parts undergoing a kaleidoscopic array of simultaneous non linear interactions."} As the behavior of the whole system is non-linear, the usual mathematical techniques of linear approximation such as, linear regression, normal coordinates, mean field approaches, and the like make little progress in the analysis of complex adaptive systems. As because different interactions between agents are simultaneous, parallel computing is helpful in term of simulating and analyzing these systems. 
	\item \textsl{``The impact of these systems in human affairs centers on the aggregate behavior, the behavior of the whole."}
	\item \textsl{``The interactions evolve over time, as the parts adapt in an attempt to survive in the environment provided by the other parts."}
	\item \textsl{``Complex adaptive systems anticipate."}
\end{enumerate}

@@

\subsubsection{Criteria}
Echo has been constructed on a set of criterion. The following is a short summary on it extracted from Holland's \textsl{Hidden Order: How Adaptation Builds Complexity} \cite{holland1996}.

@@

\section{Conclusion}
This chapter discusses the field of science that takes concepts from evolutionary biology to solve and optimize problems in compute science. It also discusses the interdisciplinary field Artificial life where scientist discuss diverse knowledge from biology, economics, physics and use computer science to simulate and analyze these science. The discussion of this chapter is expected to provide a base upon which the following chapters will begin construction of the core discussion of this thesis.
